% Write your abstract here. This should summarize the entire project including objectives, methods, and outcomes. It should be complete one full page.

With the fast growth of Artificial Intelligence (AI) and Large Language Models (LLMs), there is an increasing need for smart systems that go beyond simple reactions to engage users in a proactive and personalized way. Traditional AI systems mainly rely on single-model designs. They offer fixed responses with little adaptability and cannot remember user-specific context over time. These limitations reduce their effectiveness in situations that require ongoing interaction, personalization, and smart decision-making. 

This project suggests creating a proactive multi-agent orchestration framework based on LLMs to support intelligent, context-aware user engagement. The system includes several specialized agents—such as conversational, analytical, recommendation, and evaluation agents—working together through an orchestration layer. This design allows the system to manage tasks dynamically, share responsibilities among agents, and create coherent and contextually relevant outputs. A key part of the system is persistent user profiling, which captures and updates user preferences, interaction history, and behavior patterns to support personalized responses. The proposed system can start interactions proactively, analyze user-generated content like documents and text, create meaningful outputs such as questions, summaries, topic mappings, and personalized feedback. It also supports ongoing learning by using past interactions to improve future recommendations and insights. The modular and scalable design ensures efficient deployment and real-time performance, making it suitable for real-world applications. 

The implementation especially targets educational use cases, where the system helps learners by creating study materials, assessing understanding, and offering tailored learning paths. %Experimental evaluations show that the multi-agent approach improves interaction quality, enhances personalization, and leads to better content comprehension compared to traditional single-agent systems. 

Overall, this project emphasizes the potential of multi-agent LLM-based systems to change user engagement by enabling proactive, smart, and adaptive interactions in various fields.